Learning, Evaluation and Recognition of \strips\ Action Models with Classical Planning

### 2018-04-16 doc/aij18/related_work.tex
Added other comparison tables

>>>>

\begin{table}
	\small
	\centering
	\begin{tabular}{ l | c | c | c |}
		& \multicolumn{1}{|p{2cm}|}{Plan traces (PO states)}
		& \multicolumn{1}{|p{2cm}|}{Plan traces (PO actions)}
		& \multicolumn{1}{|p{2cm}|}{Plan traces (PO both)}   \\
		\hline			
		ARMS & \checkmark & & \\
		AMAN & \checkmark & & \\
		CAMA & \checkmark & & \\
		LAMP & \checkmark & & \\
		SLAF & \checkmark & & \\
		LOCM & \checkmark & & \\
		FAMA & \checkmark & \checkmark & \checkmark \\
	\end{tabular}
	\caption{PO=Partial Observability, FO=Full Observability}
	\label{table:input_comparison2}
\end{table}

\begin{table}
	\small
	\centering
	\begin{tabular}{ l | c | c |}
		& States 
		& Actions  \\
		\hline
		LOCM & zero & FO\\		
		ARMS & zero or PO & FO \\
		AMAN & PO & FO \\
		CAMA & PO & FO \\
		LAMP & PO & FO \\
		SLAF & PO & FO \\		
		FAMA & zero or PO & zero or PO \\
	\end{tabular}
	\caption{PO=Partial Observability, FO=Full Observability}
	\label{table:input_comparison3}
\end{table}
